---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gliomaData

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/llrs/gliomaData.svg?branch=master)](https://travis-ci.org/llrs/gliomaData)
[![Lifecycle: dormant](https://img.shields.io/badge/lifecycle-dormant-blue.svg)](https://www.tidyverse.org/lifecycle/#dormant)
<!-- badges: end -->

The goal of gliomaData is to provide data for RGCCA vignettes.

## Installation

You can install the released version of gliomaData from [GitGhub](https://github.com/llrs/gliomaData) with:

```{r, eval=FALSE}
remotes::install_github("llrs/gliomaData")
```

The original version of the data can be found [here](http://biodev.cea.fr/sgcca/).

You might get an error installing like this and might need to download the tar.gz file and then install it from there. 

## Examples

Some data provided by the package:

```{r}
library(gliomaData)
data(clinic)
clinic[1:5, 1:10]
```
